CommonMind Consortium: DLPFC

### 2020-09-17 combined_analysis/diff.networks.Rmd
Update diff networks

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(plyr) 
library(qvalue)  
}) 
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

@@

```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=500}

i = which(df_cohort2$FDR < 0.05)[1:20]

>>>>

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(plyr) 
library(qvalue)  
library(BiocParallel)  
}) 
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, BPPARAM=SerialParam())  
```

@@

```{r modules.in.second.cohort.Dx, fig.width=8, fig.height=100}

i = which(df_cohort2$FDR < 0.05)[1:10]
